---
title: "678 final"
author: "xiaoyanbin Cai"
date: "2022-12-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Background
I decided to choose the data set that includes the information on the number of testes of individuals for COVID-19 infection performed in New York City beginning March 1, 2020 which was the date that COVID-19 was first identified in the state.

#Loading library
```{r}
library(tidyverse)
library(ggplot2)
library(boot)
library(car)
#library(readxl)
library(lme4)          
library(lmerTest) 
library(plyr) 
library(Hmisc)
```

#Importing data
```{r}
airbnb <- read.csv("~/Desktop/678-final-project/airbnb.csv")#Import data
summary(airbnb)#check the summary of the data
type <- unique(airbnb$neighbourhood)#to see how many groups are in the data
#NYC_19 <- read.csv("~/Desktop/678-final-project/New_York_State_Statewide_COVID-19_Testing.csv")
#head(NYC_19)
#summary(NYC_19)#summary to see the overall information about this dataset. So that would be more clear for me to know which variables should I analiezed,

#my_data <- read_excel("~/Desktop/678-final-project/climate.xlsx")
```

## Including Plots

You can also embed plots, for example: I'm trying to do visualization about cumulative number of tests performed in NYC to that would be more straight forward to see.

```{r}
#Using ggplot to see the cumulative number of tests performed of different counties in NYC.
ggplot(NYC_19, aes(x = Cumulative.Number.of.Tests.Performed,fill=County)) +
    geom_histogram(bins=5) +
    ggtitle("cumulative # of test performed in NYC in differnt counties")
```

```{r}
#making some simple 
ggplot(NYC_19, aes(x = New.Positives, y = Cumulative.Number.of.Positives, color = County)) +
  geom_point(show.legend = FALSE) +
  #geom_point(bins=5)+
  facet_wrap(~County)
```



```{r}
#Forming linear regression between cumulative number of positives and new positives
model <- glm(Cumulative.Number.of.Positives ~ New.Positives, data = NYC_19, family = poisson)
#glm.diag.plots(model)
# output plots in a 2 x 2 grid 
par(mfrow = c(2,2)) 

# diagnostic plots
plot(model)
summary(model)
avPlots(model)
```
# As we can see from above, they do not look like good expression of regression. Since there's doesn't have cloud-like shape on residuals 

```{r}

#model_2 <- glm(Cumulative.Number.of.Positives, # formula
             #data = NYC_19, # dataset
             #family = ("gaussian")) # fit a poisson model

# output plots in a 2 x 2 grid 
#par(mfrow = c(2,2)) 

# diagnostic plots
#plot(model_2)
```

```{r}
# plot & add a regression line
ggplot(NYC_19, aes(x = New.Positives, y = Cumulative.Number.of.Positives)) + # draw a 
    geom_point() + # add points
    geom_smooth(method = "glm", # plot a regression...
    method.args = list(family = "poisson")) # ...from the binomial family
```
#As we can see the above linear regression, data are not quite fit the linear regression. So that this might not be a proper linear regression of this data.

```{r}
#Data preparation
nyc19_imeans <- ddply(NYC_19, "Test...Positive",
                       positive_trait = mean(Cumulative.Number.of.Positives, na.rm=TRUE),
                       test_trait = mean(Test...Positive, na.rm=TRUE))
describe(nyc19_imeans)
```

```{r}

```

