---
title: "678 final"
author: "xiaoyanbin Cai"
date: "2022-12-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
tinytex::reinstall_tinytex(repository = "illinois")
```

## Data Background
I decided to choose the Airbnb data set that related to Masachuesstt as my

#Loading library
```{r}
library(tidyverse)
library(ggplot2)
library(lme4)          
library(lmerTest) 
library(plyr) 
library(kableExtra)
library(dplyr)
library(leaflet)
library(coefplot)
library(tinytex)
```

##Importing data
```{r}
airbnb1 <- read.csv("~/Desktop/678-final-project/airbnb.csv")#Import data
airbnb2 <- read.csv("~/Desktop/678-final-project/13.6.2022.csv")
airbnb3 <- read.csv("~/Desktop/678-final-project/20.3.2022.csv")
airbnb4 <- read.csv("~/Desktop/678-final-project/17.12.2021.csv")
airbnb5 = dplyr::bind_rows(airbnb1,airbnb2,airbnb3,airbnb4)#to combine all the airbnb data in MA
summary(airbnb5)#check the summary of the raw data
#As we can see from summary, there're some NA values in neighbourhood_group and reviews_per_month.


type <- unique(airbnb5$neighbourhood)#to see how many groups are in the data
head(airbnb5)
```
##Basic data information and data cleaning
```{r}
kable(head(airbnb5[,c(1:3,6,9:11:12,14:17)]))#extract the main data columns that I need to analyze
airbnb6 = airbnb5[,c(1:3,6,9:11:12,14:17)]
summary(airbnb6)#check the summary of the new data frame
Airbnb = na.omit(airbnb6)#elimate NA values in data set
Airbnb <- Airbnb %>%
  filter(Airbnb$price > 0)
Airbnb2 <- Airbnb %>%
  filter(Airbnb$number_of_reviews > 0)
Airbnb2$id = as.character(Airbnb2$id)
Airbnb2$host_id = as.character(Airbnb2$host_id)
length(Airbnb2$price)
```
*As we can see from new data frame summary, there're some NA values in neighbourhood_group and reviews_per_month. So that I need to elimate all the NA values that include in price and number_of_reviews. After that we get 10957 results in total

##Table about room type
```{r}
kable(table(Airbnb2$room_type))
```
*As we can see from above,home/apt has the largest number in the table which is 6937. So that we can see how the relationship between the most-used room type and the price.

## EDA
```{r}
plot1 <- ggplot(data = Airbnb2, aes(x = number_of_reviews, y = price, color = room_type)) +
    geom_line()+
  ggtitle("Relationship between price and # of reviews of different room type")
show(plot1)
   
plot2 <- ggplot(data = Airbnb2, aes(x = number_of_reviews, y = price)) +
    geom_line() +
    facet_wrap(facets = vars(room_type))  
show(plot2)
```
*I made two linear graphs about relation between price and number of reviews of different room types. As we can see from 'plot2'entire home/apt has the most number of reviews and change of price is relative stable than that of other room type. And for shared room which has the most small number of reviews and the price of shared room is almost the same.

```{r}
#Fig of average number of reviews per neighbourhood
ggplot(data=Airbnb2, aes(x=neighbourhood, y= number_of_reviews))+geom_bar(stat = "identity",  fill = "pink") + ggtitle("Average number of reviews per neighbourhood")+ylab("Frequency of reviews") + theme(axis.text.x = element_text(angle = 30, hjust = 1))
```
*As we can see from the graph above, Allston has the highest number of reviews and East Boston is second highest and Dorchester is the third one.

*Fig of average price per neighbourhood
```{r}
ggplot(data=Airbnb2, aes(x=(neighbourhood), y= price))+geom_bar(stat = "identity",  fill = "pink") + ggtitle("Average price per neighbourhood")+ylab("Average price") + theme(axis.text.x = element_text(angle = 30, hjust = 1))
```
*Fig of distribution of number of reviews
```{r}
ggplot(Airbnb2, aes(number_of_reviews))+ geom_histogram(binwidth = 5,color = "black", fill = "sky blue")+ ggtitle("Distribution of number of reviews") + ylab ("frequency of reviews") + xlab("number of review")+ theme(axis.text.x = element_text(angle = 0, hjust = 1))+ xlim(0,200)
```
*According to the graph above, we can see that the majority of airbnb have less than 100 reviews 

*#Using leaflet to make a map of Airbnb in MA
```{r}
Boston_area_map <- leaflet(airbnb5) %>%
  addTiles() %>%
  addCircleMarkers(lng = airbnb5$longitude,
                   lat = airbnb5$latitude)
show(Boston_area_map)
```

*To see how the correlation between price and minimum nights. Because higher price may affect the number of reviews.
```{r}
cor <- cor.test(Airbnb2$minimum_nights,Airbnb2$price,
                method="pearson")
cor
```
*The p-value is 2.105e-14. So it reject the null hypothesis. So the correlation between price and minimum nights is significant. I might want to add the correlation term into the model to test whether this influence is significant.

*Distribution of room price
```{r}
ggplot(Airbnb2, aes(price))+ geom_histogram(binwidth = 50, color = "light yellow", fill = "orange")+ ggtitle(" Distribution of room price") + ylab ("Frequency of price") + xlab("Price") + theme(axis.text.x = element_text(angle = 0, hjust = 1))+xlim(0,1000)
```

*Since from the graph above, price does not present as normal distribution so that I need to do the log transformation.
```{r}
price_t <- Airbnb2%>%
  mutate(logprice = log(price))
ggplot(Airbnb2, aes(log(price)))+ geom_histogram(binwidth = 0.25, color = "light yellow", fill = "orange")+ ggtitle("Distribution of room price") + ylab ("Frequency of transformedprice") + xlab("log(Price)") + theme(axis.text.x = element_text(angle = 0, hjust = 1))+ xlim(2,8)
```
*Visualize the relationship between logprice and minimum nights
```{r}
ggplot(price_t, aes(x = logprice, y = minimum_nights)) +
  geom_point() +
  stat_smooth()
```
*As we can see from the graph above, the graph does not suggest a linearly increasing relationship between the logprice and minimum nights. So the assumption that lower price may lead to more days to stay may not be a right assumption
##Modeling
*Doing model 1 of Simple Linear Regression
```{r}
model_1 = lm(logprice ~ room_type + number_of_reviews + minimum_nights + number_of_reviews_ltm+reviews_per_month+ calculated_host_listings_count+availability_365, data = price_t) 
summary(model_1)
plot(model_1)#create a residual plot and Q-Q plot.
coefplot(model_1,title = "Coefficient plot for model 1")
```


```{r}
model_2 = lmer(logprice ~ room_type + (1|neighbourhood)-1, data =  price_t)
summary(model_2)
coefplot(model_2, title = "Coefficient plot for model 2")
```
```{r}
model_3 = lmer(logprice ~ room_type + minimum_nights + (0 + minimum_nights|neighbourhood)-1, data =  price_t)
#display(model3)
coefplot(model_3,title = "Coefficient plot for model 3")
```

```{r}
model_4 = lmer(logprice ~ room_type + minimum_nights + (1 + minimum_nights|neighbourhood)-1, data =  price_t)
#display(model3)
coefplot(model_4,title = "Coefficient plot for model 4")
```

```{r}
anova(model_2, model_3,model_4,refit = FALSE) #anova test.
plot(fitted(model_4),resid(model_4,type="pearson"),col="orange", main = "Fig 13. residual plot for model4")
abline(h =0)
```

